{\includegraphics[width=3cm, height=2.5cm]{Cran.jpg}} \\ \includegraphics[width=7cm, height=1cm]{TB.jpg} \\ {Technical Documentation for TersectBrowser+}

### 2025-05-02 TechDoc/TechDoc.tex
added to future extension work

\subsubsection{Test Results}
\subsubsection{Future Improvements}

@@

\subsubsection{Test Results}
\subsubsection{Future Improvements}
\subsection{Future Work and Extension Design}
\subsubsection{Automated Introgression Search Extension}

>>>>

\subsubsection{Test Results}

\subsubsection{Future Improvements}
Currently, only bins on the TersectBrowser+ heatmap are highlighted in red to indicate the positions of high-impact variants. Highlighting could be extended across the Genome Browser and Gene Models extension, so that gene models matching the parameters of the feature search query are also highlighted in red.

@@

\subsubsection{Test Results}
\subsubsection{Future Improvements}
Currently, barcode viewing is limited to the downloaded file. It can be extended to display barcodes in the popup window, with the variant highlighted in red.

\subsection{Future Work and Extension Design}
\subsubsection{Automated Introgression Search Extension}
